Nic Steyn

### 2025-04-02 site/papers.qmd
added temporally aggregated paper to research outputs

>>>>

### 2025

Ogi-Gittins, I., **Steyn, N.**, Polonsky, J., Hart, W. S., Keita, M., Ahuka-Mundeke, S., Hill, E. M., & Thompson, R. N. (2025). Simulation-based inference of the time-dependent reproduction number from temporally aggregated and under-reported disease incidence time series data. *Philosophical Transactions of the Royal Society A*. [http://doi.org/10.1098/rsta.2024.0412](https://royalsocietypublishing.org/doi/10.1098/rsta.2024.0412)
